The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
Updates based on feedback
Disc draft

\smallskip \noindent
\textbf{Performance  }
%Define
Performance changes are defined to be types of change that intentionally alter system performance.
%Data and examples
No evidence of performance driven changes were identified in the API.
%Conclusion
This therefore leads us to conclude that API evolution is not driven by performance changes.

@@

\subsection{Discussion RQ1}

@@

\subsection{Discussion RQ2}

\subsection{Discussion RQ3}

>>>>

\smallskip \noindent
\textbf{Performance  }
%Define
Performance changes are defined to be types of change that intentionally alter system performance.
%Data and examples
No evidence of performance-driven changes were identified in the API.
%Conclusion
This therefore leads us to conclude that API evolution is not driven by performance changes.

@@

\subsection{RQ1 Answer}  
RQ1: What drives API evolution?

%Answer to RQ
Talk about the results regarding the law of familiarity that didn't apply.

%Point to results

%Relate to literature
Cite the papers that say u shoulnt change APIs and say that our results agree \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers} 
Explain our results with this: 
       1. The laws are not immutable, since they arise from the habits and practices of humans. [1980programs]
       2. If laws governing large-program evolution can be formulated at all, they must certainly be weaker than those formulated in the biological sciences, where regularity stems from the collective behavior of cellular systems that, even though alive, are nonintelligent, i.e., are not influenced by conscious thought processes, at least at the level of human understanding. [On Understanding Laws, Evolution, and Conservation in the Large-Program Life Cycle]

"1.1 Give a clear answer to the RQ. (Reject null / alternative)"

"1.2 Point to results"
%      -Bring up the most interesting/distinct trends

"1.3 Compare to literature (i.e. relate to previous work)"
 %      -Do our results agree with prev. work?

\subsection{RQ2 Answer}
RQ2: How reverse engineer?

%1.1 Give a clear answer to the RQ. (Reject null / alternative)

%1.2 Point to results
%      -Bring up the most interesting/distinct trends

%1.3 Compare to literature (i.e. relate to previous work)
 %      -Do our results agree with prev. work?

\subsection{Contribution to Academia} 
%       -How will our study help other researchers?
%       -How are the results valuable?

\subsection{Contribution to Practice}
%       -How will our study help Axis? (More important)
The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed. [1980programs]

The main thing will be:
1. Our results found that feedback loop is, a) very importnat and b) the main thing that Axis wants to improve
2. Relate to Swanson/Chapin saying the types help to budget/plan and facilitate communication between stakeholders
       [quotes re. budget/plan]:

       [quotes re. communication/stakeholders]:

---------------------------------------------

%       -How will our study help other companies? (Less important)

%Discuss and evaluate conflicting explanations of the results. This is the sign of a good discussion.

@@
